### 2019-10-11 inst/vign/taxize_vignette.Rmd

Instead of a full classification, you may only want a single name, say a family name for your species of interest. The function *tax_name} is built just for this purpose. As with the `classification` function you can specify the data source with the `db` argument, either ITIS or NCBI.

@@

I may happen that a data source does not provide information on the queried species, than one could take the result from another source and union the results from the different sources.

>>>>

Instead of a full classification, you may only want a single name, say a family name for your species of interest. The function `tax_name` is built just for this purpose. As with the `classification` function you can specify the data source with the `db` argument, either ITIS or NCBI.

@@

It may happen that a data source does not provide information on the queried species, than one could take the result from another source and union the results from the different sources.
